Title Goes Here

### 2025-04-21 analysis/paper/paper.qmd
XRD refinement dataset mutated to present percentages.

# Read grouped supporting data
xrd_perc <- read_csv('data/xrd_data/xrd_goals.csv') # File with component percentage of all samples for annotations
xrd_marks <- read_csv('data/xrd_data/xrd_peaks.csv') # File with peak data and d spacing for plot labels

# Read individual xrd files
sp15_xrd <- read_csv('data/xrd_data/SP15_xrd.csv')
sp58_xrd <- read_csv('data/xrd_data/SP58_xrd.csv')
sp62_xrd <- read_csv('data/xrd_data/SP62_xrd.csv')
sp69_xrd <- read_csv('data/xrd_data/SP69_xrd.csv')

@@

>>>>

# Read grouped supporting data
xrd_perc <- read_csv('analysis/data/raw_data/xrd_data/xrd_goals.csv') # File with component percentage of all samples for annotations
xrd_marks <- read_csv('analysis/data/raw_data/xrd_data/xrd_peaks.csv') # File with peak data and d spacing for plot labels

# Read individual xrd files
sp15_xrd <- read_csv('analysis/data/raw_data/xrd_data/SP15_xrd.csv')
sp58_xrd <- read_csv('analysis/data/raw_data/xrd_data/SP58_xrd.csv')
sp62_xrd <- read_csv('analysis/data/raw_data/xrd_data/SP62_xrd.csv')
sp69_xrd <- read_csv('analysis/data/raw_data/xrd_data/SP69_xrd.csv')

@@

# Turn value from percent table to percentages
xrd_perc <- xrd_perc %>%
  mutate(`Content (%)` = round(`Content (%)` * 100, 4))

### 2025-04-21 analysis/supplementary-materials/appendix1.qmd
XRD refinement dataset mutated to present percentages.

# Read grouped supporting data
xrd_perc <- read_csv('data/xrd_data/xrd_goals.csv') # File with component percentage of all samples for annotations
xrd_marks <- read_csv('data/xrd_data/xrd_peaks.csv') # File with peak data and d spacing for plot labels

@@

# Read individual xrd files
sp6_xrd <- read_csv('data/xrd_data/SP6_xrd.csv')
sp7_xrd <- read_csv('data/xrd_data/SP7_xrd.csv')
sp10_xrd <- read_csv('data/xrd_data/SP10_xrd.csv')
sp14_xrd <- read_csv('data/xrd_data/SP14_xrd.csv')
sp18_xrd <- read_csv('data/xrd_data/SP18_xrd.csv')
sp21_xrd <- read_csv('data/xrd_data/SP21_xrd.csv')
sp28_xrd <- read_csv('data/xrd_data/SP28_xrd.csv')
sp30_xrd <- read_csv('data/xrd_data/SP30_xrd.csv')
sp33_xrd <- read_csv('data/xrd_data/SP33_xrd.csv')
sp34_xrd <- read_csv('data/xrd_data/SP34_xrd.csv')
sp40_xrd <- read_csv('data/xrd_data/SP40_xrd.csv')
sp50_xrd <- read_csv('data/xrd_data/SP50_xrd.csv')
sp52_xrd <- read_csv('data/xrd_data/SP52_xrd.csv')
sp57_xrd <- read_csv('data/xrd_data/SP57_xrd.csv')
sp59_xrd <- read_csv('data/xrd_data/SP59_xrd.csv')
sp61_xrd <- read_csv('data/xrd_data/SP61_xrd.csv')
sp63_xrd <- read_csv('data/xrd_data/SP63_xrd.csv')
sp66_xrd <- read_csv('data/xrd_data/SP66_xrd.csv')

@@

```{r}
#| label: fig-xrd-sp18
#| fig-cap: Plot of minerals identified through XRD in the Lower Jurassic (Carixian) chert sample from the outcrop Praia do Belixe (SP18_PBX). The rhombus shape signifies main peaks key to identify each mineral. Labels represent the d spacing values of key mineral peaks.

>>>>

# Read grouped supporting data
xrd_perc <- read_csv('analysis/data/raw_data/xrd_data/xrd_goals.csv') # File with component percentage of all samples for annotations
xrd_marks <- read_csv('data/xrd_data/xrd_peaks.csv') # File with peak data and d spacing for plot labels

# Turn value from percent table to percentages
xrd_perc <- xrd_perc %>%
  mutate(`Content (%)` = round(`Content (%)` * 100, 4))

@@

# Read individual xrd files
sp6_xrd <- read_csv('data/xrd_data/SP6_xrd.csv')
sp7_xrd <- read_csv('data/xrd_data/SP7_xrd.csv')
sp10_xrd <- read_csv('data/xrd_data/SP10_xrd.csv')
sp14_xrd <- read_csv('data/xrd_data/SP14_xrd.csv')
sp18_xrd <- read_csv('analysis/data/raw_data/xrd_data/SP18_xrd.csv')
sp21_xrd <- read_csv('data/xrd_data/SP21_xrd.csv')
sp28_xrd <- read_csv('data/xrd_data/SP28_xrd.csv')
sp30_xrd <- read_csv('data/xrd_data/SP30_xrd.csv')
sp33_xrd <- read_csv('data/xrd_data/SP33_xrd.csv')
sp34_xrd <- read_csv('data/xrd_data/SP34_xrd.csv')
sp40_xrd <- read_csv('data/xrd_data/SP40_xrd.csv')
sp50_xrd <- read_csv('data/xrd_data/SP50_xrd.csv')
sp52_xrd <- read_csv('data/xrd_data/SP52_xrd.csv')
sp57_xrd <- read_csv('data/xrd_data/SP57_xrd.csv')
sp59_xrd <- read_csv('data/xrd_data/SP59_xrd.csv')
sp61_xrd <- read_csv('data/xrd_data/SP61_xrd.csv')
sp63_xrd <- read_csv('data/xrd_data/SP63_xrd.csv')
sp66_xrd <- read_csv('data/xrd_data/SP66_xrd.csv')

@@

```{r}
#| label: fig-xrd-sp18
#| fig-cap: Plot of minerals identified through XRD in the Lower Jurassic (Carixian) chert sample from the outcrop Praia do Belixe (SP18_PBX). The rhombus shape signifies the main peaks key to identify each mineral. Labels represent the d spacing values of key mineral peaks.
